Robustness of MinD oscillation in \emph{Escherichia coli} with diverse cell shapes

### 2014-11-07 paper/paper-MinD.tex
changes with Jeff on abstract Tested everything on bennet.

\begin{article}
\begin{abstract}
  The dynamics of the Min-protein system help \emph{Escherichia coli}
  regulate the process of cell division by identifying the center of
  the cell.  While this system usually exhibits robust polar
  oscillations in a variety of cell shapes, new experiments have shown
  that when the cells are mechanically deformed into wide, flattened
  out, irregular shapes, the spatial regularity of these oscillations
  breaks down. Here we study widely used stochastic and deterministic
  models of Min-system simulation within these new cell shapes.  We
  find that the deterministic model is decidedly inadequate to
  reproduce the experimentally observed behavoir, while the stochastic
  model, based on the same differential equations, is able to do so
  accurately.  We also find that it is the flattening rather than the
  irregularity and asymmetry of the cell shape that causes the
  irregular oscillation behavoir.
\end{abstract}

>>>>

\begin{article}
\begin{abstract}
  The dynamics of the Min-protein system help \emph{Escherichia coli}
  regulate the process of cell division by identifying the center of
  the cell.  While this system usually exhibits robust bipolar
  oscillations in a variety of cell shapes, recent experiments have
  shown that when the cells are mechanically deformed into wide,
  flattened out, irregular shapes, the spatial regularity of these
  oscillations breaks down. We employ widely used stochastic and
  deterministic models of the Min system to simulate cells with flattened
  shapes.  The deterministic model predicts strong bipolar
  oscillations, in contradiction with the experimentally observed
  behavoir, while the stochastic model, which is based on the same
  reaction-diffusion equations, does predict spatially irregular
  oscillations as observed in experiment.  We further report
  simulations of symmetric but flattened cell shapes, and find that it
  is the flattening rather than the asymmetry of the cell shapes that
  causes the irregular oscillation behavoir.
\end{abstract}
